### 2019-02-07 1-Preamble/4-Acknowledgement/acknowledgement.tex
Added list of publications
Starting to fill the sections of each chapters, to have an overview of the organization

And I would like to acknowledge ...

See https://perso.crans.org/besson/phd/thanks/

\TODO{To start!}

>>>>

\TODO{To finish}
% See https://perso.crans.org/besson/phd/thanks/

And I would like to acknowledge and thank the following people.

My PhD advisors, \href{https://moychristophe.wordpress.com/}{Christophe Moy} and \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{Émilie Kaufmann}.

My family: my parents, Christophe and Patricia, my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian} and my younger brother Fabian, Marine, my grand-parents, Jeannine, Jean-Marc and Jacqueline, my uncle and aunt Jacques, Bernadette, and my cousin Lara.

My closest friends, sorted in an absurd chronological list: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia, Julia, Pierre, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément, Jill-Jênn, Alain, Claire, Édouard, Loïc, Damien, Kumudham, Priscilla, Thibault, Sébastien, Sélim, Valentin, Marine, Johanne, Lola.

My wonderful colleagues during these three years: Rémi, Pascal, Yves, Jacques, Ali, Haïfa, Marwa, Navik, Quentin, Vincent, Rami, Muhammad, Cristo, Adrien, Esteban, Ali, Éloïse, Bastien, Corentin, Georgios, in Rennes ; and Ronan, Odalric-Ambrym, Philippe, Olivier, Florian, Xuedong, Guillaume, Julien, Mathieu, Matteo, Mahsa, Nicolas in Lille.

Thanks to some people for their support: Karine, Jeannine, Grégory, Anne and others at CentraleSupélec Rennes; François, David, David at ENS de Rennes, Romaric at ENSAI, Amélie at Inria Lille, Amélie at Lycée Chateaubriand.
During my studies at ENS Cachan (now Paris-Saclay), I am thankful to all the great professors who taught me, including Frédéric, Alain and Claudine in the maths department, Sylvain, Paul, Serge in the computer science department, and thanks to Carine, Delphine and the late Nicolas for their support.

I would also like to thank some things. First, the Earth, then my \href{https://perso.crans.org/besson/zero-dechet/}{bike} which I enjoyed riding everyday despite the too many accidents.
My \href{https://perso.crans.org/besson/cuisine/}{culinary friends}: cheese, chocolate, coffee, vegetables etc!
My \href{https://perso.crans.org/besson/}{technological friends}: Bash, Python, XUbuntu, Firefox, Konsole, Visual Studio Code etc.

Some friends thanked me in their own PhD thesis, and it is a pleasure to do the same.
In a chronological order, I thank
%,
\href{http://jill-jenn.net/}{Jill-Jênn Vie} (\href{http://jiji.cat/cat.pdf}{thesis}), \href{https://navikkumarmodi.wordpress.com/}{Navikkumar Modi} (\href{https://tel.archives-ouvertes.fr/tel-01668536/document}{thesis}), \href{https://quentinbodinier.wordpress.com/}{Quentin Bodinier} (\href{https://tel.archives-ouvertes.fr/tel-01731022/document}{thesis}), \href{https://paris-sorbonne.academia.edu/FBesson}{Florian Besson}, \href{https://sites.google.com/view/guerand}{Jessica Guérand} (\href{https://drive.google.com/open?id=17CBibM8ZlzIbyVxpxktK3j5rNePALUs8}{thesis}), \href{https://sites.google.com/view/ducasse/}{Romain Ducasse} (\href{https://drive.google.com/open?id=1u2oxRRimcO0jQfuYwSVwgKfcHU5DdoPK}{thesis}), \href{https://members.loria.fr/SAbelard/}{Simon Abelard} (\href{https://members.loria.fr/SAbelard/theseabelard.pdf}{thesis}), \href{http://www.cmap.polytechnique.fr/~sacchelli/}{Ludovic Sacchelli} (\href{https://tel.archives-ouvertes.fr/tel-01893068/document}{thesis}), \href{http://pages.saclay.inria.fr/claire.brecheteau/}{Claire Brécheteau} (\href{https://hal.archives-ouvertes.fr/tel-01897787/document}{thesis}), \href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/}{Damien Allonsius} (\href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/documents/recherche/these/Main.pdf}{thesis}), \href{https://remibonnefoi.wordpress.com/}{Rémi Bonnefoi}, Rami Othman.

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année.
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.

### 2019-02-07 2-Chapters/3-Chapter/chapter3.tex
Okay, all the template is better for my need now. I have to write…
Starting to fill the sections of each chapters, to have an overview of the organization

% First chapter begins here
\chapter{Chapter 2 Title}
\label{chapter:2}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

% ----------------------------------------------------------------------------
\section{Blabla}
\label{sec:blabla}

>>>>

% First chapter begins here
\chapter{Presentation of SMPyBandits, a Complete MAB Simulation Library}
\label{chapter:3}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/3-Chapter/Images/}}

This chapter is intended as a long version of the paper presenting SMPyBandits that I wrote in Summer 2018, see https://hal.inria.fr/hal-01840022

% ----------------------------------------------------------------------------
\section{Presentation of the library}
\label{sec:3:presentationLibrary}

I want to show what is SMPyBandits, what problems does it solve, what did I implement, how to use it.

% ----------------------------------------------------------------------------
\section{Review of state-of-the-art single-player algorithms}
\label{sec:3:reviewSPAlgorithms}

I want to show that SMPyBandits contains highly documented implementations of all the most important algorithms designed for stationary single-player multi-armed bandit.

I will include here formulas about the main algorithms (klUCB, MOSS, etc).
I will pick some problems (Bernoulli, Gaussian, others), with fixed means or ``Bayesian'' means (\ie, changing at each time) and I will run extensive numerical simulations to compare the main algorithms.

The take away message is: klUCB beats UCB, Thompson sampling is great too, all the others algorithms are less efficient or comparable, so we only use klUCB for all the rest of this thesis.

I will include graphs showing the mean regret $R_t$ as a function of time $t$, as well as histograms or boxplots showing the distribution of $R_T$.

% ----------------------------------------------------------------------------
\section{Some numerical experiments to compare time and memory costs of various algorithms}
\label{sec:3:timeAndMemoryCosts}

I want to show the real numerical costs in terms of computation time and storage requirement of the various algorithms for single-player bandits.

Maybe I can pick one simple problem family (\eg, evenly spaced in $[\varepsilon,1-\varepsilon]$), and run experiments for $T=1000,5000,10000$ etc, and $K=2,3,5,9,20,30,50,100,1000$ and show the evolution of time/memory as a function of $T$ and $K$.

The goal is to highlight that the simplest (but most efficient) algorithms have a memory cost bounded by $\bigO{K}$ and a time complexity at each time step $t\in[T]$ bounded by $\bigO{K}$, independent of $t$.

% ----------------------------------------------------------------------------
\section{An example of another model: rested or restless Markov models}
\label{sec:3:markovModels}

Maybe if I have space at the end of this chapter, I can show another part of the library, maybe introduce the rested/restless Markov models (with maybe just one example) and show simulations in this model?

SMPyBandits also implemented sparse MAB models (with $s<K$ arms with a mean $\mu_i>0$ and $K-s$ arms with a mean $\mu_i \leq 0$), I could also present this model, the various algorithms designed to tackle it, and some numerical experiments.

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 3}
\label{sec:3:conclusion}

In this chapter, we saw...

Future works include...

### 2019-02-07 2-Chapters/4-Chapter/chapter4.tex
Okay, all the template is better for my need now. I have to write…
Starting to fill the sections of each chapters, to have an overview of the organization

% First chapter begins here
\chapter{Chapter 3 Title}
\label{chapter:3}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/3-Chapter/Images/}}

% ----------------------------------------------------------------------------
\section{Blabla}
\label{sec:blabla}

>>>>

% First chapter begins here
\chapter{Multi-Armed Bandits Models for Internet of Things Networks}
\label{chapter:4}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/4-Chapter/Images/}}

This chapter has three sections, each is a raw include from different papers

- ``Multi-Armed Bandit Learning in IoT Networks and non-stationary settings'', see https://hal.inria.fr/hal-01575419

- ``MALIN: Multi-Arm bandit Learning for Iot Networks with GRC: A TestBed Implementation and Demonstration that Learning Helps'', demo at ICT, and the companion paper ``GNU Radio Implementation of MALIN: "Multi-Armed bandits Learning for Internet-of-things Network"'', see https://hal.inria.fr/hal-02006825

- ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \verb{https://perso.crans.org/besson/articles/BMBM__IEEE_WCNC_2019.pdf}

% ----------------------------------------------------------------------------
\section{A first model of learning devices in an IoT network}
\label{sec:4:firstModel}

- ``Multi-Armed Bandit Learning in IoT Networks and non-stationary settings'', see https://hal.inria.fr/hal-01575419

% ----------------------------------------------------------------------------
\section{Test-bed implementation of our model for real-world validation}
\label{sec:4:gnuradio}

- ``MALIN: Multi-Arm bandit Learning for Iot Networks with GRC: A TestBed Implementation and Demonstration that Learning Helps'', demo at ICT, and the companion paper ``GNU Radio Implementation of MALIN: "Multi-Armed bandits Learning for Internet-of-things Network"'', see https://hal.inria.fr/hal-02006825

% ----------------------------------------------------------------------------
\section{Extension of our model to account for retransmissions}
\label{sec:4:retransmissions}

- ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \verb{https://perso.crans.org/besson/articles/BMBM__IEEE_WCNC_2019.pdf}

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 4}
\label{sec:4:conclusion}

In this chapter, we saw...

Future works include...

### 2019-02-07 2-Chapters/6-Chapter/chapter6.tex
Okay, all the template is better for my need now. I have to write…
Starting to fill the sections of each chapters, to have an overview of the organization

% First chapter begins here
\chapter{Chapter 5 Title}
\label{chapter:5}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/5-Chapter/Images/}}

% ----------------------------------------------------------------------------
\section{Blabla}
\label{sec:blabla}

>>>>

% First chapter begins here
\chapter{Towards Non-Stationary Models}
\label{chapter:6}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/6-Chapter/Images/}}

This chapter is basically a raw include from my paper ``The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits'', see https://hal.inria.fr/hal-02006471

% ----------------------------------------------------------------------------
\section{The piece-wise non-stationary bandits model}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{The Bernoulli Generalized Likelihood Ratio Test}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{The GLRklUCB Algorithm}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{Regret analysis for the GLRklUCB alRegret analysis for the GLRklUCB algorithm}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{Numerical simulations for piece-wise stationary bandit problems}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{Conclusion of Chapter 6}
\label{sec:6:conclusion}

In this chapter, we saw...

Future works include...

% ----------------------------------------------------------------------------
\appendix

\section{FIXME appendix in a chapter: where is it?}
